---
title: "Measurement & Statistics 3-year plan"
author: "Russell Almond"
date: "2023-06-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## About this Schedule

For the purposes of planning, we (the Measurement & Statistics faculty) put together a 3-year plan of what courses we will be offering.  There is, however, uncertainty associated with these plans.  In particular, the farther out in time, the more likely that there will be changes.  Hopefully, it should be good enough for planning.

```{bash}
curl https://pluto.coe.fsu.edu/CourseLists/MandSThreeYearPlan.xlsx > MandS3YearPlan.xlsx

```

```{r grabSchedule, echo=FALSE}

schedule <- readxl::read_xlsx("MandS3YearPlan.xlsx","Plan")
faculty <- readxl::read_xlsx("MandS3YearPlan.xlsx",2)
courses <- readxl::read_xlsx("MandS3YearPlan.xlsx","courses")
semesterName <- unique(paste(schedule$Semester,schedule$Year))

```

## Three Year Plan {.tabset .tabset-pill}

### `r semesterName[1]`

```{r echo=FALSE}
i <- 1
schedule %>% filter(Semester==Semester[i],Year==Year[i])
```


### `r semesterName[2]`

```{r echo=FALSE}
i <- 2
schedule %>% filter(Semester==Semester[i],Year==Year[i])
```

### `r semesterName[3]`
```{r echo=FALSE}
i <- 3
schedule %>% filter(Semester==Semester[i],Year==Year[i])
```

### `r semesterName[4]`
```{r echo=FALSE}
i <- 4
schedule %>% filter(Semester==Semester[i],Year==Year[i])
```

### `r semesterName[5]`
```{r echo=FALSE}
i <- 5
schedule %>% filter(Semester==Semester[i],Year==Year[i])
```

### `r semesterName[6]`
```{r echo=FALSE}
i <- 6
schedule %>% filter(Semester==Semester[i],Year==Year[i])
```

### `r semesterName[7]`
```{r echo=FALSE}
i <- 7
schedule %>% filter(Semester==Semester[i],Year==Year[i])
```

### `r semesterName[8]`
```{r echo=FALSE}
i <- 8
schedule %>% filter(Semester==Semester[i],Year==Year[i])
```

### `r semesterName[9]`
```{r echo=FALSE}
i <- 9
schedule %>% filter(Semester==Semester[i],Year==Year[i])
```

## Course Descriptions

## Faculty

Tenure line faculty:

* _Russell Almond_
* _Huan (Hailey) Kuan_
* _Yanyun Yang_
* _Qian (Jackie) Zhang_. (pronounced "Chyan Jang")

Adjuncts:

* _Salih Binichi_
* _Suleyman Olgar_
* _Ying Zhang_ 
* _Ambiguatus Staff_ -- This prolific instructor is well versed in skills, however, he always manages to bow out to be replaced with somebody else before the class starts.

## Courses

EDF5400	Des/Inf Statistics Apps 
EDF5401	Gen Linear Models Apps 
EDF5402	Adv Topics in ANOVA 
EDF5404	Bayesian data analysis
EDF5406	Multivariate Analysis Apps 
EDF5409	Causal Modeling
EDF5432	Measurement Theory I 
EDF5434	Measurement Theory II
EDF5435	Scaling and Equating
EDF5448	Scale and Instrument Development
EDF5484	Ed Data Analysis
EDF7418	Multilevel Modeling
EDF7489	Meta-analysis
EDF6937	Seminar: Adv Structural equation modeling
EDF6937	Seminar: Educational Data Mining
EDF6937	Seminar: Longitudinal data analysis
EDF6937	Seminar: Mediation and Moderation
EDF5419	Missing Data Analysis
EDF5922	Ed Psych Colloquium


## Questions



